### 2022-12-27 response.tex

\paragraph{How does {\justicia} outperform a direct approach by learning a Bayesian Network on limited samples?} We agree with the reviewer that learning a Bayesian Network on limited samples does not always result in a better robustness (e.g., less standard deviation of fairness metrics estimation) of {\justicia} than the direct approach of estimating fairness on a dataset.

Elaborately, in Chapter~\ref{chapter:justicia} Figure~\ref{fairness_justicia_fig:sample-size}, {\justicia} demonstrates higher robustness than the direct approach, where we consider a specific distribution of non-sensitive features conditioning only on sensitive features. Thus, Figure~\ref{fairness_justicia_fig:sample-size} does not involve experiments with Bayesian Network capturing correlations of all features, which we indeed introduce later in Chapter~\ref{chapter:fvgm}. In our revised experiment, we observe that {\justicia} with Bayesian network, called {\fvgm}, exhibits less robustness due to Bayesian network learning.

\paragraph{Clarification on Fairness Influence Function (FIF).} Our additive axiom for FIFs is based on the idea of decomposing the total unfairness of the classifiers among different subsets of features~\cite{begley2020explainability,lundberg2020explaining}. We consider that the sum of FIFs of all subsets of non-sensitive features is equal \textit{to the resultant unfairness of the classifier}, where unfairness is a real number in $ [0,1] $, such as statistical parity, equalized odds, and predictive parity.

\paragraph{Clarification on Bayesian Network.} We consider a Bayesian network as an input distribution to express the conditional dependencies and independencies among features. In Chapter~\ref{chapter:CNF_feature_correlation}, we demonstrate the encoding of probabilistic inference into SSAT via additional Boolean variables and clauses~\cite{chavira2008probabilistic}. We also discuss the complexity of the SSAT encoding in terms of the complexity of the Bayesian network (ref.~\ref{chapter_fairness_preliminaries_BN}, page 15).

### 2022-12-27 chapters/appendix.tex
updated response

\chapter{Feature Correlations in SSAT-based Fairness Verifier: {\justicia}}
\label{sec:CNF_feature_correlation}
In Chapter~\ref{chapter:justicia}, {\justicia} verifies the fairness of CNF classifiers without considering correlation among features. In this chapter, we address fairness verification of CNF classifiers with correlated features. In particular, we present the encoding of conditional probabilities from a Bayesian network into the SSAT formulation in {\justicia}.

>>>>

\chapter{Feature Correlations in SSAT-based Fairness Verifier: {\justicia}}
\label{chapter:CNF_feature_correlation}
In Chapter~\ref{chapter:justicia}, {\justicia} verifies the fairness of CNF classifiers without considering correlation among features. In this chapter, we address fairness verification of CNF classifiers with correlated features. In particular, we present the encoding of conditional probabilities from a Bayesian network into the SSAT formulation in {\justicia}.
